Sex-Based Differences in Tuberculosis Immune Response: The Role of Leptin

### 2025-05-02 products/manuscript/Manuscript.qmd
Final Change

@@

```{r}
#| label: tbl-coef
#| tbl-cap: "Coefficient estimation (95% CI) from linear regression and Poisson regression."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table2.png"))
```

@@

```{r}
#| label: tbl-ma
#| tbl-cap: "Mediation analysis with estimated effects and 95% CI."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table3.png"))
```

@@

```{r}
#| label: fig-rf
#| fig-cap: "Parameter tuning results of random forest. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure3.png"))
```

```{r}
#| label: fig-rt
#| fig-cap: "Parameter tuning results of regression tree. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure4.png"))
```

@@

```{r}
#| label: fig-rfrt
#| fig-cap: "Comparison of random forest and regression tree: predicted values vs. observed values. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure5.png"))
```

@@

```{r}
#| label: fig-rfsim
#| fig-cap: "Parameter tuning results of random forest model using simulated data. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure6.png"))
```

```{r}
#| label: fig-rfpredsim
#| fig-cap: "Fitting results of random forest on simulated data: predicted values vs. observed values. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure7.png"))
```

>>>>

## Data cleaning

Due to measurement instability, a small number of participants had total body water (TBW) values recorded as less than 0 or greater than 0.70, which are biologically implausible. As TBW serves as a foundational parameter for calculating other body composition indices, participants with TBW values outside the plausible range (<0 or >0.73) were excluded from downstream analyses to ensure data quality and the validity of derived measures. In addition, percentage-based indices such as body water and body fat were originally recorded in decimal format and were converted to percentage format (e.g., 0.45 to 45%) to enhance interpretability. CD4+ and CD8+ cell counts were rounded to the nearest integer to reflect the typical reporting standard in clinical and immunological research.

@@

```{r}
#| label: tbl-coef
#| tbl-cap: "Coefficient estimation (95% CI) from linear regression and Poisson regression. Fat mass index is only included in the linear regression model, while both predictors are included in the Poisson regression model to assess medication effects."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table2.png"))
```

@@

```{r}
#| label: tbl-ma
#| tbl-cap: "Mediation analysis with estimated effects and 95% CI. For negative direct effect or indirect effect, the percentage of mediated effect cannot be calculated due to model setting."
#| echo: FALSE
knitr::include_graphics(here("results","tables","table3.png"))
```

@@

```{r}
#| label: fig-rf
#| fig-cap: "Parameter tuning results of random forest. Darker square means lower root mean squared error."
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure3.png"))
```

```{r}
#| label: fig-rt
#| fig-cap: "Parameter tuning results of regression tree. Darker square means lower root mean squared error. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure4.png"))
```

@@

```{r}
#| label: fig-rfrt
#| fig-cap: "Comparison of random forest and regression tree: predicted values vs. observed values. The dashed black line on the diagonal denotes the reference where predicted values are equal to observed values. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure5.png"))
```

@@

```{r}
#| label: fig-rfsim
#| fig-cap: "Parameter tuning results of random forest model using simulated data. Darker square means lower root mean squared error. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure6.png"))
```

```{r}
#| label: fig-rfpredsim
#| fig-cap: "Fitting results of random forest on simulated data: predicted values vs. observed values. The dashed black line on the diagonal denotes the reference where predicted values are equal to observed values. "
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure7.png"))
```
